
\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}



\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{:\newline#2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingPosition}[2]{
  \vspace{2pt}
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


\begin{document}
%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Mert Uygur} & Email : \href{mailto:mertuygr@gmail.com}{mertuygr@gmail.com}\\
  \color{blue}
  \href{https://github.com/mertuygr}{Github} 
  \color{black}
  And 
  \color{blue}  
  \href{https://www.linkedin.com/in/mertuygur/}{Linkedin} & Mobile : +905353148462
\end{tabular*}

%-----------SUMMARY-----------------
\section{Summary}
Software Engineer with 3 years of experience in object-oriented software development and
testing. Worked with medium to large groups of developers. Familiar with software
development processes such as Agile/Scrum.

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\href{https://www.ayesas.com/en}{AYESAS}}{Ankara, Turkey}
      {Software Engineer}{Dec. 2016 - Present}
      \resumeItemListStart
        \resumeItem{Decoy Launching System}
          {\begin{itemize}
              \item Responsible for building central control software which operates the on-board decoy launchers in a frigate warship with other development team members using \textbf{Java}.
              \item Implemented software modules of \textbf{OSGi} application using the Blueprint Container specification and \textbf{Maven}.
              \item Worked alongside customers to analyze customer needs and planned agile sprints that includes tasks for their requirements.
              \item Managed, merged and updated code through \textbf{Git}. Configured \textbf{Linux} based \textbf{distributed system} machines to run Java applications within the system startup and start communication among multiple machines including a one with no VGA and an only serial port.
              \item Implemented a \textbf{C++} \textbf{JNI} wrapper to make calls to a dynamic library within the Java application. 
              \item Configured \textbf{TeamCity} server that automates build infrastructure.
          \end{itemize}    
          }
        \resumeItem{Link 16 - Tactical Data Link Processor}
         {
         \begin{itemize}
             \item Contributed to the development of tactical data link software that runs on embedded system (\textbf{Integrity RTOS}) as a part of an avionic system. \item Was responsible for implementation and debugging of communication component of the Link 16 project with \textbf{C++}.
             \item Maintained \textbf{Doxygen} formatted documentation for source code of project. 
             \item\textbf{SVN} and \textbf{JIRA} used to coordinate efforts among the developers and testers.
             \item Was a member of a team that integrated the software into the avionics system.
         \end{itemize} 
         }
         \resumeItem{Utility Helicopter Digital Map Software}
          {\begin{itemize}
              \item Tested mission-critical firmware and software on a new product development team. 
              \item Developed and maintained automated test infrastructure in \textbf{C++} and \textbf{Qt} for regression testing.
              \item Practiced \textbf{Agile} and \textbf{Scrum} in 2 week sprints with 10 other developers.
          \end{itemize}
          }
      \resumeItemListEnd


  \resumeSubHeadingListEnd



%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Middle East Technical University}{Ankara, Turkey}
    {Master of Science in Computer Engineering}{Sep. 2018 -- January 2021}
  \resumeSubheading
    {Bilkent University}{Ankara, Turkey}
    {Bachelor of Science in Computer Engineering}{Sep. 2012 -- June 2016}
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
